%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{hyperref}

% only for pdflatex
% \input{glyphtounicode}

% fontawesome
\usepackage{fontawesome5}

% fixed width
\usepackage[scale=0.90,lf]{FiraMono}

% light-grey
\definecolor{light-grey}{gray}{0.83}
\definecolor{dark-grey}{gray}{0.3}
\definecolor{text-grey}{gray}{.08}

\DeclareRobustCommand{\ebseries}{\fontseries{eb}\selectfont}
\DeclareTextFontCommand{\texteb}{\ebseries}

% custom underilne
\usepackage{contour}
\usepackage[normalem]{ulem}
\renewcommand{\ULdepth}{1.8pt}
\contourlength{0.8pt}
\newcommand{\myuline}[1]{%
  \uline{\phantom{#1}}%
  \llap{\contour{white}{#1}}%
}


% custom font: helvetica-style
\usepackage{tgheros}
\renewcommand*\familydefault{\sfdefault} 
%% Only if the base font of the document is to be sans serif
\usepackage[T1]{fontenc}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{0in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting - serif
% \titleformat{\section}{
%   \vspace{2pt} \scshape \raggedright\large % header section
% }{}{0em}{}[\color{black} \titlerule \vspace{-5pt}]

% TODO EBSERIES
% sans serif sections
\titleformat {\section}{
    \bfseries \vspace{2pt} \raggedright \large % header section
}{}{0em}{}[\color{light-grey} {\titlerule[2pt]} \vspace{-4pt}]

% only for pdflatex
% Ensure that generate pdf is machine readable/ATS parsable
% \pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-1pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & {\color{dark-grey}\small #2}\vspace{1pt}\\ % top row of resume entry
      \textit{#3} & {\color{dark-grey} \small #4}\\ % second row of resume entry
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      #1 & {\color{dark-grey}} \\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

% CHANGED default leftmargin  0.15 in
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{0pt}}

\color{text-grey}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge Basavaraja V} \\ \vspace{5pt}
    \small \faPhone* \texttt{+918971126783} \hspace{1pt} $|$
    \hspace{1pt} \faEnvelope \hspace{2pt} \texttt{basavarajavyadav@gmail.com} \hspace{1pt} $|$ 
    \href{https://linkedin.com/in//}{\raisebox{-0.2\height}\faLinkedin\ {royaldevops}} $|$
    \href{https://github.com/}{\raisebox{-0.2\height}\faGithub\ {rajdeveloper}} $|$
     \href{https://www.hackerearth.com/@basavarajav/}{\raisebox{-0.2\height}\ {Hackerearth}} $|$
    \hspace{1pt} \faMapMarker* \hspace{2pt}\texttt{India}
    \\ \vspace{-3pt}
\end{center}

%-----------EXPERIENCE-----------
\section{EXPERIENCE}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Futorix Solutions Pvt. Ltd.}{11-March-2019 -- Present}
      {Fullstack Developer}{Bangalore, India}
      \resumeItemListStart
        \resumeItem{Developed both web and mobile application for the employee operations such as On boarding, Personal Information, Performance Management, Attendance, Leave, Finance Information, \textbf{Payroll}, Separation, etc.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------

\section{PROJECTS}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Payroll}} {}
          \resumeItemListStart
            \resumeItem{Designed payroll for three clients across India and Maldives.}
            \resumeItem{It involves six cycles such as Initiate, Retro, Run, Hold, Confirmation, Generate Payslip Cycles respectively.}
            \resumeItem{\textbf{Initiate:} This cycle selects the eligible employees set from attendance and compensation for the current month.}
            \resumeItem{\textbf{Retro:} It is similar to initiate but it selects the eligible employees set from attendance and compensation for the previous months.}
            \resumeItem{\textbf{Run:} It computes the pay, deduction and taxable(PT, PF, Itax) items respectively.}
            \resumeItem{\textbf{Hold:} It put the selected employees in hold.}
            \resumeItem{\textbf{Confirmation:} This cycle confirm previous cycles after reconcile.}
            \resumeItem{\textbf{Generate Payslip:} It generates the payslip.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------PERSONAL PROJECTS-----------

\section{PERSONAL PROJECTS}
    \resumeSubHeadingListStart
           \resumeProjectHeading
          {\textbf{Crack It}} {}
          \resumeItemListStart
            \resumeItem{A Trivia android app for General Knowledge MCQ using flutter. Available in the play store. \href{https://play.google.com/store/apps/details?id=com.royaldeveloper.crackit}{\raisebox{-0.2\height}\ {(Crack It)}}}
          \resumeItemListEnd
            \resumeProjectHeading
          {\textbf{Recall App}} {}
          \resumeItemListStart
            \resumeItem{Recall App is a ML App to analysis the whatsapp chat history of two users using flutter and python and it generates the statistics. Available in the play store. \href{https://play.google.com/store/apps/details?id=com.royaldevops.recallapp}{\raisebox{-0.2\height}\ {(Recall App)}}}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------PUBLICATIONS-----------

\section{PUBLICATIONS}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Journal}}{}
          \resumeItemListStart
            \resumeItem{Lokesh Nandanwar, Palaiahnakote Shivakumara, Swati Kanchan, \textbf{V Basavaraja}, Devanur S Guru, Umapada Pal, Tong Lu, Michael Blumenstein, \textbf{"DCT-phase statistics for forged IMEI numbers and air ticket detection"}, Published in Expert Systems with Applications Volume 164, February 2021, 114014, Publisher Pergamon.}
          \resumeItemListEnd
          
        \resumeProjectHeading
          {\textbf{Conference }}{}
          \resumeItemListStart
            \resumeItem{\textbf{V Basavaraja}, Palaiahnakote Shivakumara, DS Guru, Umapada Pal, Tong Lu, Michael Blumenstein \textbf{"Age estimation using disconnectedness features in handwriting"}, Published in International Conference on Document Analyses and Recognition (ICDAR 2019), Publisher IEEE.}
            \resumeItem{Palaiahnakote Shivakumara, \textbf{V Basavaraja}, Harsha S Gowda, DS Guru, Umapada Pal, Tong Lu \textbf{"A new RGB based fusion for forged IMEI number detection in mobile images"}, published in 2018 16th International Conference on Frontiers in Handwriting Recognition (ICFHR) Publisher IEEE.}
          \resumeItemListEnd
      
%-----------EDUCATION-----------
\section {EDUCATION}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Mysore}{Aug. 2015 -- July 2018}
      {Master of Computer Applications}{Mysore, Karnataka}
      	\resumeItemListStart
    	\resumeItem {\textbf{Coursework}: Data Structures, Algorithms, Databases, Computer Systems, Machine Learning.}
        \resumeItemListEnd
  \resumeSubHeadingListEnd

%
%-----------PROGRAMMING SKILLS-----------
\section{SKILLS}
 \begin{itemize}[leftmargin=0in, label={}]
    \small{\item{
     \textbf{Stacks} {: Python, JavaScript (Nodejs, Angular, Ionic), Flutter, HTML/CSS, LaTeX, SQL (PostgreSQL).}\vspace{2pt} \\
     \textbf{Tools}     {: VScode, Figma, Trello, Bitbucket, Jupyter Notebook, Google Colab, etc.}\\
     \textbf{DevOps}     {: AWS-EC2, S3 Bucket, SES, SNS, Lambda Functions, Rekognition, etc.}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
